%% Package and Class "uiucthesis2014" for use with LaTeX2e.
\documentclass[edeposit,fullpage,hidelinks]{uiucthesis2018}


\usepackage[acronym,toc]{glossaries}
\usepackage{listings}
\usepackage{minted}
\usepackage{appendix}

\usepackage{xspace}
\usepackage{graphics}

\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}
\newcommand{\SaltProc}{\textsc{SaltProc}\xspace}
\newcommand{\OpenMC}{\textsc{OpenMC}\xspace}
\newcommand{\SerpentTWO}{\textsc{Serpent2}\xspace}
\newcommand{\ONIX}{\textsc{ONIX}\xspace}
\newcommand{\NJOYTWOONE}{\textsc{NJOY21}\xspace}
\newcommand{\ChemTriton}{\textsc{ChemTriton}\xspace}
\newcommand{\Shift}{\textsc{Shift}\xspace}
\newcommand{\SCALE}{\textsc{SCALE}\xspace}
\newcommand{\TRITON}{\textsc{TRITON}\xspace}
\newcommand{\ORIGEN}{\textsc{ORIGEN}\xspace}
\newcommand{\MCNPSIX}{\textsc{MCNP6}\xspace}
\newcommand{\CINDERNINETY}{\textsc{CINDER90}\xspace}
\newcommand{\ADDER}{\textsc{ADDER}\xspace}

\usepackage{placeins}
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF

\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{subfig}
\usepackage{hhline}
\usepackage{amsmath}
\usepackage{color}
\usepackage{multirow}
\usepackage{siunitx} % typesetting for units
\usepackage{tabulary}
\usepackage[version=4]{mhchem}
\sisetup{
    input-decimal-markers = .,input-ignore = {,},table-number-alignment = right,
    group-separator={,}, group-four-digits = true
}
\usepackage{booktabs}
\newcommand\tab[1][1cm]{\hspace*{#1}}

\usepackage{threeparttable, tablefootnote}

%tikzpicture fit to page width
\usepackage{environ}
\makeatletter
\newsavebox{\measure@tikzpicture}
\NewEnviron{scaletikzpicturetowidth}[1]{%
  \def\tikz@width{#1}%
  \def\tikzscale{1}\begin{lrbox}{\measure@tikzpicture}%
  \BODY
  \end{lrbox}
  \pgfmathparse{#1/\wd\measure@tikzpicture}%
  \edef\tikzscale{\pgfmathresult}%
  \BODY
}

\usepackage{tabularx}
\newcolumntype{b}{>{\hsize=1.0\hsize}X}
\newcolumntype{q}{>{\hsize=0.5\hsize}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash\hsize=0.5\hsize}X}
\newcolumntype{z}{>{\hsize=0.75\hsize}X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\newcolumntype{m}{>{\hsize=.75\hsize}X}

\usepackage{cleveref}
\usepackage{datatool}
\usepackage[numbers]{natbib}
\usepackage{notoccite}


\usepackage{tikz}
\usetikzlibrary{positioning, arrows, decorations, shapes}

\usetikzlibrary{shapes.geometric,arrows}
\tikzstyle{process} = [rectangle, rounded corners, minimum width=2.5cm, minimum height=1cm,text centered, draw=black, fill=blue!30]

\tikzstyle{object} = [ellipse, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=green!30]
\tikzstyle{objectr} = [ellipse, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]

\tikzstyle{empty} =  [rectangle, rounded corners, minimum width=2.5cm, minimum height=0.7cm,text centered, draw=black, fill=white!30]
\tikzstyle{arrow} = [thick,->,>=stealth]


\title{Implementation and validation of \OpenMC depletion capabilities in \SaltProc}
\author{Oleksandr Redin Yardas}
\department{Nuclear, Plasma, Radiological Engineering}
\schools{B.A., Grinnell College, 2020}
\msthesis
\advisor{Madicken Munk}
\degreeyear{2023}
\committee{Dr. Madicken Munk, Advisor \\ Professor Tomasz Kozlowski}

\renewcommand{\lstlistingname}{Code}% Listing -> Algorithm

\begin{document}
\include{acros}
\maketitle

\frontmatter
%% Create an abstract that can also be used for the ProQuest abstract.
%% Note that ProQuest truncates their abstracts at 350 words.
\begin{abstract}
No operating molten salt reactors (MSRs) exist, so we must rely on computer simulations
to study this technology. Popular MSR designs to use in simulations
include the Molten Salt Breeder Reactor (MSBR), the Molten Salt Reactor Experiment
(MSRE), and the Molten Salt Fast Reactor (MSFR). A key process to
consider for MSRs is on-line fuel reprocessing and its effect on reactor
dynamics. \SaltProc is an open source interface code tool that simulates on-line
fuel reprocessing when coupled with a depletion-capable transport solver.
\SaltProc was intended to be usable with any depletion solver, but initially was written
with support for \SerpentTWO exclusively. In this work, I overhauled the \SaltProc code
to simplify coupling supports for depletion solvers and added support for \OpenMC.
To ensure that the code maintained existing functionality as well as extended it, I
validated the new functionality on a full-core model of the MSBR. In this work, I find
$k_\text{eff}$ between \OpenMC and \SerpentTWO differ by +35 pcm at beginning of life
and by 700 pcm at the end of the simulation after one year of operation. I also find
that the relative difference of most actinides is less than 2\%. The actinides
with smaller concentrations in the fuel tend to have larger relative differences
between the two codes. I find similar results for fission products, however, the 
relative difference is smaller, with most of the fission products having a
relative difference no greater than 0.6\%. There are some outliers in the results
with very high relative errors, however, these can be attributed to numerical errors.
This is significant as this makes \SaltProc the first completely open-source tool to
flexibly and accurately simulate on-line fuel reprocessing.
\end{abstract}

\chapter*{Acknowledgments}

This manuscript is the culmination of hundreds of hours of work, a substantial
amount of which is not my own. I would like to thank Dr. Madicken Munk and Dr.
Paul Romano for their guidance and mentorship, and for opening my eyes to the
complexity, frustrations, and joys of software development. I would also like to
thank Dr. Tomasz Kozlowski for his thorough feedback and critical perspective
that have vastly improved the quality of this manuscript. I would also like to
thank the Nuclear Regulatory Commission for funding this work through the NRC
Integrated University Grant Program Fellowship.

This research made use of Idaho National Laboratory computing resources which
are supported by the Office of Nuclear Energy of the U.S. Department of Energy
and the Nuclear Science User Facilities under Contract No. DE-AC07-05ID14517.

I would also like to thank my Advanced Reactors and Fuel Cycles peers,
particularly Amanda Bachmann, Samuel Dotson, and Luke Seifert for their code
reviews and knowledge on nuclear systems, Python, and molten salt reactors. And
to Andrei Rykhlevskii, thank you for creating \SaltProc and for your response to
my probing questions. To the NPRE Staff who run the show behind the scenes, you
are awesome and are the ones who make this whole show work. I would especially
like to thank Scott Dalby for always being a friendly face, and Kristie
Stramaski, for her reasoned and fast responses to my sometimes panicked emails.

In my personal life, I am extremely fortunate to have the boundless love and
support of my mother, Zanna, and father, David, and for that I have endless
gratitude. To my brother, Nico, and sister, Sophie, thank you for showing me
different ways of being. To my partner BJ and my friends in OAC, I am so
thankful to have met you all during my time in Illinois. You have made it all
the more bearable.

Finally, I would like to thank Dr. Kathryn Huff for allowing me to join ARFC and
start on this journey. While we haven't had much time to work together, I am
thankful for meeting her and reigniting my optimism for the future of nuclear
power.

%% The thesis format requires the Table of Contents to come
%% before any other major sections, all of these sections after
%% the Table of Contents must be listed therein (i.e., use \chapter,
%% not \chapter*).  Common sections to have between the Table of
%% Contents and the main text are:
%%
%% List of Tables
%% List of Figures
%% List Symbols and/or Abbreviations
%% etc.

\tableofcontents
\listoftables
\listoffigures

%% Create a List of Abbreviations. The left column
%% is 1 inch wide and left-justified
%\chapter{List of Abbreviations}
%\printglossaries
%% Create a List of Symbols. The left column
%% is 0.7 inch wide and centered

\pagebreak
\mainmatter

\input{chapter1_intro}
\input{chapter2_litreview}
\input{chapter3_implementation}
\input{chapter4_model}
\input{chapter5_results}
\input{chapter6_conclusions}

\backmatter

\bibliographystyle{apalike}
\bibliography{bibliography}

\mainmatter
\appendix
\input{appendix}

\end{document}
\endinput
%%
%% End of file `thesis-ex.tex'.
